Certified Desugaring of Javascript Programs using Coq

### 2016-12-15 paper/paper.tex
Some changes to lambdajs described.

\asi{describe the changes to the language.}

For the purpose of relating the two semantics, we first developed a
formalization of the \lambdajs core language. This was necessary because no such
formalization existed previously; a formalization of the original, ES3-based
\lambdajs was available\cite{github:brownplt/LambdaJS}, but the two
versions of \lambdajs differ too much for this to be useful.

We decided to formalize the \lambdajs core using a
pretty-big-step semantics, as in JSCert, to make the job of
relating the two semantics easier. We have also developed
an interpreter for \lambdajs, which we proved sound and
complete with respect to the pretty-big-step semantics.
The proof script was developed using domain-specific tactics,
which made it simple and robust.

@@

% This was moved.
%At this stage we stumbled upon an interesting performance issue 
%involving the Coq proof assistant. The proof of completeness required
%inverting the pretty-big-step semantics judgment; this turned out
%to be very slow, and also generated large proof terms, which increased
%the memory footprint. The problem is well-known~\cite{Monin:Coq2}; 
5our solution involved
%precomputing the required inversion principles using
%\texttt{Derive Inversion}, and using the precomputed inversion
%principles to create a specialized inversion tactic.

@@

\section{Issues found}

>>>>

Because of the various issues we found in \lambdajs as defined
in~\cite{Politz-al:DLS12} and which we detail in Section~\ref{sec:issues},
we decided to revise the language. The full list of changes is
detailed in~TODO\mm{Can we just link the wiki page? Or should we use an appendix?}, we present some of them below.
\begin{itemize}
\item The attribute access and modification operators, which tried to directly
    model the operators from JavaScript, were removed. We found that the complexities
    of attribute access is much better handled in the desugaring.
\item We removed the imperative features of the language which do not involve the
    object heap. This change simplified the definition of the semantics, which made
    the proofs easier.
\item We added a new primitive value named \texttt{empty}, which models the empty
    completion value of JavaScript, and a second kind of the semicolon operator,
    which returns the last non-empty value of its subexpressions. This allowed to
    correctly implement statement completion values in a natural way.
\item An integer datatype was added. Even though ES5 itself has no integers,
    they are used in the definition of the binary operators (bitwise logical operators,
    bit shifting).
\end{itemize}

For the purpose of relating the semantics of \lambdajs and ES5, we developed a
formalization of the \lambdajs core language. This was necessary because no such
formalization existed previously; a formalization of the original, ES3-based
\lambdajs was available\cite{github:brownplt/LambdaJS}, but the two
versions of \lambdajs differ too much for this to be useful.

We decided to formalize the \lambdajs core using a
pretty-big-step semantics, as in JSCert, to make the job of
relating the two semantics easier. We have also developed
an interpreter for \lambdajs, which we proved sound and
complete with respect to the pretty-big-step 
semantics.\footnote{The initial version of the interpreter was
written by Martin Lorentz.}
The proof script was developed using domain-specific tactics,
which made it simple and robust.

@@

% This was moved.
%At this stage we stumbled upon an interesting performance issue 
%involving the Coq proof assistant. The proof of completeness required
%inverting the pretty-big-step semantics judgment; this turned out
%to be very slow, and also generated large proof terms, which increased
%the memory footprint. The problem is well-known~\cite{Monin:Coq2}; 
%our solution involved
%precomputing the required inversion principles using
%\texttt{Derive Inversion}, and using the precomputed inversion
%principles to create a specialized inversion tactic.

@@

\section{Issues found}
\label{sec:issues}
